A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-07-28 idetc2018_journal.tex
Professor's change

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.

@@

\section{Introduction}
\begin{figure}
\centering
\includegraphics[width=200pt]{figure/fig_circuit_defect.eps}
  \caption{The mechanism synthesis problem for the prescribed motion.
  The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
\label{circuit_defect}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figure/overall_approach.eps}
  \caption{The Machine Learning approach begins by creating an invariant signature for the path and the motion data, which facilitates a compact and hierarchical clustered database and an auto-encoder Neural Network trained to elicit good, defect-free solutions or subjected to local, fast optimization. The results are astonishingly good, defect-free concept design solutions for input problems.}
\label{overallMethod}
\end{figure*}

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
In the majority of methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.

\subsection{Motivation}
The majority of mechanism synthesis methods are based on the precision point approach.
This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
The defect in a mechanism renders itself useless for its intended application.
The defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.

Let's see an example of this in a motion generation task.
The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just being a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.

Thus, we present a perceptive way of synthesizing defect free linkages for motion and path generation problems.
%As a guiding direction to advance state of the art, we propose following criteria for an effective mechanism synthesis method,
%  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
%\end{enumerate}
To capture the complete prescribed task, we represent it as a continuous parametric curve.
The objective is to find a linkage, that has a coupler motion or path compatible with the task.
We developed the compatibility measure in a way that is invariant to similarity transformations.
Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
The motivation behind using clustered database is rooted in the broader objective of machine design.
Mechanism synthesis is a part of the conceptual design phase, which is one of the earliest stages of product design cycle of a machine.
Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
The method only deals with the coupler curves and is indifferent to the linkage type.
Thus, it is readily scalable to any type of planar linkage.
In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in the Fig.~\ref{circuit_defect}.

\subsection{Literature Survey and Overview}
% Global search methods
Instead of brute-force search within tolerance regions, some approaches apply separate constraints to take care of the defects and form an optimization problem of Non-Differentiable objective function.
It can be solved by metaheuristic algorithms like Differential-evolution(DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem.
Ebrahimi and Payvandy\cite{Ebrahimi2015} presented an application of Imperialist Competitive Algorithm (ICA) for synthesizing path generating four-bars having desired workspace limits.
Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
The above methods can produce many defect-free solutions and are scalable to any type of linkages.
However, these methods tend to be slow and inefficient as they start from scratch for every instance with no guarantee of converging to an acceptable solution.

Path synthesis methods based on Fourier analysis do take the continuity information of coupler path into account.
However, most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
They use a combination of global and local search methods for optimizing Fourier Deviant function to compute the dimensions of planar four-bar linkages without an initial guess.
Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation of four-bar mechanisms.
In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used curvature of the coupler curve for path synthesis using Genetic Algorithms.
Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
% ---

% Atlas Based Methods ---
Instead of the global search, an alternative approach is to start from a good initial guess based on an atlas and use local search methods.
We adopt this approach and combine with our novel formulation to generate a diverse set of concept solutions.
McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on the harmonic analysis.
Wandling\cite{wandling2000} has presented an atlas-based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
The best match is returned as the solution to the input.
Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
Then, we perform compact clustering of the data using machine learning techniques.
A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve that represents all the segments in it.
This is because our representation facilitates part-to-whole matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
%  ---

The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
we employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

The original contributions in the paper are as follows:
1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis.

%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Signatures of Coupler Path and Motion}\label{sec_sign}
Focus of the paper is on a novel method for mechanism synthesis that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input, and returns defect-free linkages that produce similar motion or path.
The input is transformed into a representation, termed as a signature, which is invariant to similarity operations, viz. reflection, rotation, translation, and scaling.
Signatures for path and motion are termed as path signature and motion signature, respectively.
For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].

Curvature $\kappa(t)$ of the path $(x:x(t), y:y(t))$ and its integral $K(t)$ is given by,
\begin{eqnarray}
  \kappa(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
  K(t) = \int^{t}_0 |\kappa(t)|dt \label{kInt},
\end{eqnarray}
where $\dot{x}(t)$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting}.
We compute $\kappa(t)$ and $K(t)$ along the direction of $t$, using Eq.~\req{curvatureEq} and Eq.~\req{kInt} respectively.
Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
It can be seen that the curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out. It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_bspline.eps}
  \caption{a) The path of the input motion along with direction of parametrization. b) Motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
\label{bsplineFitting}
\end{figure}

@@

Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $\kappa$ vs $K$ in Fig~\ref{signature}(a).
This is done by finding the parameter values of $t$ where $K$ changes uniformly.
For practical purposes, we find an array of the parameter $t$ such that $K$ increments by 0.1.
For each value of $t$ in that array, we compute $\kappa(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively.
We note that there is a one-to-one mapping between $t$ and $K$.
Although it seems natural to use dual-quaternions for representing motion and finding its signature,
it couples orientation with the path in a way, such that the signatures formed no longer remain invariant to similarity transformation.

These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
We know that curvature changes inversely to scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out. Reflection operation produces flipped path signature, but motion signature remains invariant.
Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}. It is important to note, that the signature depends on the direction of parameter $t$.
The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.

@@

\section{Signature Matching and Error Function}\label{sec_distanceMetric}
The signatures obtained in previous steps contain important information about the shape of the trajectory.
In this section, we formulate functions that evaluate the similarity between two trajectories based on their signatures.
These distance functions can be used as error metric, which can be minimized using optimization methods.

@@

Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in~\ref{wholePart}.
Let $p$ and $W$ be their signatures respectively, where $W$ completely contains $p$ as shown in Fig.~\ref{pathSignature}.
The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signatures.
The partial matching works as follows:

\begin{enumerate}
  \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
  \item $p$ is slid with offset index $j$ along $W$.
  \item For each offset $j$, we compute normalized cross-correlation\cite{lewis1995fast} function given by,
\end{enumerate}
\vspace{-0.6cm}
\begin{equation}\label{nccEq}
  Cn(j, p, W) = |\sum_{i}^{p_{sp}} \frac{(W(i+j) - \bar{W}(j : j + p_{sp}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{sp}}{(W(i+j) - \bar{W}_{p_{sp}})}^2\sum_{i}^{p_{sp}}{(p(i) - \bar{p})}^2}} |,
\end{equation}
where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{sp}$ is length of the array $p$ and $\bar{W}(j:j + p_{sp})$ is mean of the values of array $W$ between index range of ($j, j+p_{sp}$).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Synthesizing defect-free planar four-bar mechanism for the motion generation problem has proven to be a difficult problem. These defects can be one or more of branch-, circuit-, and order-defects, which render synthesized mechanisms useless to practitioners. Such defects arise from the artificial constraints of formulating the problem as a discrete precision position problem and the corresponding methods which ignore the continuity information in the input. In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively. At the heart of this approach lies an objective function which compares the motion as a whole thereby capturing designer's intent.
In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation of the given task simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations. We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known defect-free linkages, which serve as a good initial choice for further optimization. In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.

%The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
%However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
%Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
%In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
%At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing the designer's intent.
%In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
%We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
%The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
%In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
%We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.

@@

\section{Introduction}
The mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are often categorized as path, motion and function generation; see McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Path generation task aims to synthesize a mechanism which can guide a particular point of a rigid body (often, the coupler) along a prescribed path.
On the other hand, the objective of the motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is given as a time sequence of positions, whereas the prescribed motion is given as a time sequence of positions and orientations. Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem. This paper is concerned with calculating the dimensional parameters of defect-free planar four-bar mechanisms while providing machine designers a robust set of defect-free mechanism design solutions during the conceptual design phase, and thereby dramatically broadening the inventions design capabilities.

A large majority of mechanism synthesis methods are based on the precision point approach.
This approach is a clever approximation trick to solve the above-mentioned problems, where the task is discretized into precision points. These points instead of the actual task, are required to be interpolated or approximated by the designed mechanism. However, this representation loses critical information about the actual continuous task and can lead to mechanisms with the order, circuit and branch defects; see Chase and Mirth\cite{chasemirth} for a thorough discussion on such defects. Unfortunately, these defects render mechanisms useless for their intended application.
\begin{figure}
\centering
\includegraphics[width=200pt]{figure/fig_circuit_defect.eps}
  \caption{The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
\label{circuit_defect}
\end{figure}
For an example, consider a motion generation problem shown in Fig.~\ref{circuit_defect}, where the objective is to synthesize a four-bar mechanism that can perform the prescribed motion going continuously from pose\footnote{We refer to a pose as an entity that combines position and orientation.} 1 to 5. Instead of dealing with an infinite number of poses from initial to final pose, currently this problem is simplified to design a four-bar that goes through all the five poses without any guarantee on the in-between motion. Burmester~\cite{Burmester86} showed that a four-bar can go through at most five precision positions and in the best case scenario, there are a limited number of solutions. In this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}. Although it can be seen that the coupler of the four-bar passes exactly through five precision positions, it can not do so without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together and to transition from one circuit to another, the mechanism has to be taken apart and reassembled. This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, an approach proposed in the literature is to tweak precision positions in a brute-force way within some tolerance until a solution is found.
Even if a circuit defect-free solution is found, the coupler motion in-between the precision points may go through undesired poses or in an incorrect order. This is an outcome of discarding the functional aspect of continuous motion and turning the problem into an interpolation problem bereft of important details. We present our solution to the motion generation problem shown in the Fig.~\ref{circuit_defect} later on in the Case Studies section.

%As a guiding direction to advance state of the art, we propose the following criteria for an effective mechanism synthesis method,
%  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
%\end{enumerate}

% Global search methods
Instead of brute-force search within tolerance regions, some approaches apply separate constraints and form an optimization problem of non-differentiable objective function.
These methods employ metaheuristic algorithms like Differential-evolution (DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS). Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis. Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem. Ebrahimi and Payvandy\cite{Ebrahimi2015} presented an application of Imperialist Competitive Algorithm (ICA) for synthesizing path generating four-bars having desired workspace limits. Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
%The above methods can produce many defect-free solutions and are scalable to any type of linkages. However, these methods tend to be slow and inefficient as they start from scratch for every instance with no guarantee of converging to an acceptable solution.

Path synthesis methods based on Fourier analysis do take the continuity information of coupler path into account.
However, most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
They use a combination of global and local search methods for optimizing Fourier Deviant function to compute the dimensions of planar four-bar linkages without an initial guess.
Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation of four-bar mechanisms.
In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used the curvature of the coupler curve for path synthesis using Genetic Algorithms.
Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
% ---

% Atlas Based Methods ---
Instead of the global search, an alternative approach is to start from a good initial guess based on an atlas and use local search methods.
We adopt this approach and combine with our novel formulation to generate a diverse set of conceptual design solutions.
McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on the harmonic analysis.
Wandling\cite{wandling2000} has presented an atlas-based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
The best match is returned as the solution to the input.
Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figure/overall_approach.eps}
  \caption{The Machine Learning approach begins by creating an invariant signature for the path and the motion data, which facilitates a compact and hierarchical clustered database and an auto-encoder Neural Network trained to elicit good, defect-free solutions or subjected to local, fast optimization. The results are defect-free conceptual design solutions for input problems.}
\label{overallMethod}
\end{figure*}
The above methods generate data based on uniform sampling in the linkage parameter space.
Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
Then, we perform a compact clustering of the data using machine learning techniques.
A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve that represents all the segments in it.
This is because our representation facilitates part-to-whole matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
%  ---

In this paper, we represent the given task as a parametric continuous function of poses or path-points. The objective is to find a linkage which has a coupler motion or path compatible with the given task. We develop a compatibility measure invariant to similarity transformations so that position, scaling, and orientation of the given path or motion do not convolute the optimization.
Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
The motivation behind using a clustered database is rooted in the broader objectives of machine design. Mechanism synthesis is a critical part of the conceptual design phase, which requires synthesis method to be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
Our method only deals with the coupler curves and is not dependent on the linkage type.
Thus, it is readily scalable to any type of planar linkage.

The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion. We employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
A query representing an invariant signature of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

The original contributions of the paper are in 1) creating a perceptive problem formulation for path and motion generation, which solves the issues associated with the precision point approach,
%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) exploiting the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) developing a novel algorithm for partial matching of motions and paths which significantly improves the synthesis.

%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity Transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Signatures of Coupler Path and Motion}\label{sec_sign}
Focus of the paper is on a novel method for mechanism synthesis that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input, and returns defect-free linkages that produce similar motion or path.
The input is transformed into a representation, termed as a signature, which is invariant to similarity operations, viz. reflection, rotation, translation, and scaling.
Signatures for path and motion are termed as path signature and motion signature, respectively.
For calculating the path signature, we use the formulation developed by Cui et.al\cite{cui2009}.

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$, where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].

Curvature $\kappa(t)$ of the path $(x:x(t), y:y(t))$ and its integral $K(t)$ is given by,
\begin{eqnarray}
  \kappa(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
  K(t) = \int^{t}_0 |\kappa(t)|dt \label{kInt},
\end{eqnarray}
where $\dot{x}(t)$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting}.
We compute $\kappa(t)$ and $K(t)$ along the direction of $t$ using Eq.~\req{curvatureEq} and Eq.~\req{kInt}, respectively.
Figure~\ref{curvatureK} shows computed curvature and its unsigned integral for the coupler path shown in the Fig.~\ref{bsplineFitting}.
It can be seen that the curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out. It is obvious that the curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_bspline.eps}
  \caption{a) The path of the input motion along with direction of parametrization, b) motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
\label{bsplineFitting}
\end{figure}

@@

Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $\kappa$ vs $K$ in Fig~\ref{signature}(a).
This is done by finding the parameter values of $t$ where $K$ changes uniformly.
For practical purposes, we find an array of the parameter $t$ such that $K$ increments by 0.1.
For each value of $t$ in that array, we compute $\kappa(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively.
We note that there is a one-to-one mapping between $t$ and $K$.
Although it may seem natural to use planar quaternions~\cite{McCarthy90, Bottema} for representing motion and finding its signature, it couples orientation with the path in such a way that the signatures formed no longer remain invariant to similarity transformation.

These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
We know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out. Reflection operation produces flipped path signature, but motion signature remains invariant.
Figure~\ref{signature} shows the path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}. It is important to note that the signature depends on the direction of parameter $t$.
The procedure of signature calculation presented in this section is given in the Algorithm ~\ref{alg_signature}.

@@

\section{Signature Matching and Error Function}\label{sec_distanceMetric}
The signatures obtained in previous steps contain important information about the shape of the trajectory.
In this section, we formulate functions that evaluate the similarity between two trajectories based on their signatures.
These distance functions can be used as an error metric, which can be minimized using optimization methods.

@@

Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in Fig.~\ref{wholePart}.
Let $p$ and $W$ be their signatures respectively, where $W$ completely contains $p$ as shown in Fig.~\ref{pathSignature}.
The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signatures.
The partial matching works as follows:

\begin{enumerate}
  \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
  \item $p$ is slided with offset index $j$ along $W$.
  \item For each offset $j$, we compute normalized cross-correlation function~\cite{lewis1995fast}  given by,
\end{enumerate}
\vspace{-0.6cm}
\begin{equation}\label{nccEq}
  Cn(j, p, W) = |\sum_{i}^{p_{sp}} \frac{(W(i+j) - \bar{W}(j : j + p_{sp}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{sp}}{(W(i+j) - \bar{W}_{p_{sp}})}^2\sum_{i}^{p_{sp}}{(p(i) - \bar{p})}^2}} |,
\end{equation}
where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{sp}$ is length of the array $p$ and $\bar{W}(j:j + p_{sp})$ is mean of the values of array $W$ between index range of ($j, j+p_{sp}$).

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$, i.e., \emph{Part} is identical to a portion of \emph{Whole}.
